\Title

### 2022-11-30 Grimaldi-etal-BiolCybernetics.tex
2.1

	    {\bf (a)}~Given a generic raster plot defined by a set of spikes occurring on specific addresses and at specific times, one may consider that this information consists of the repeated occurrence of precise spiking motifs. 
	    {\bf (b)}~We show the motifs used in this example, each identified at the top by a different color. To each of the $10$ synapses and $71$ different possible delays is assigned an evidence of activation (red) or deactivation (blue). 
	    {\bf (c)}~The activation in time of the different motifs is then used to define a generative model for drawing a raster plot on the multi-unit address space. Note that each afferent may be connected with multiple weights at different delays. The propagation of the afferent information through these delay may generate at each time step a synchronous motif on a subset of synapses. 
	    {\bf (d)}~The output of the model provides with the predicted probability of occurrence of each motif at any time, which may be used to generate a spike as a Bernoulli trial, providing in this particular case with an exact identification of the occurrence of motifs. Knowing the results of this detection, one may for illustration purposes highlight them by different colors in the raster plots, showing that in this synthetic examples, all spikes can be annotated with each identified spiking motif. 

@@

As in a neurobiological recording or in the sensory signal representing the output of an event-based camera, any generic raster plot consists in a stream of \emph{spikes} (see Figure~\ref{fig:model}-(a)). This can be formalized as an ordered set $\event$ of addresses and timestamps $\{(\presynaddr_\arank, \timev_\arank)\}_{\arank \in [1,\numevent]}$ where $\numevent \in \mathbb{N} $ is the total number of events in the data stream and the rank $\arank$ is the index of each event. That event has a time of occurrence $\timev_\arank$  and an associated address $\presynaddr_\arank$ (which is typically in the form $(x_\arank, y_\arank, \polev_\arank)$ for event-based cameras). This defines an address space $\presynaddrspace$ which consists of the set of possible addresses. This can be the identified set of neurons in a neurobiological recording. For event-based cameras, it is denoted by $[1, \Nx]\times[1, \Ny] \times [1, \Npol] \subset \mathbb{N}^3$ where $(\Nx, \Ny)$ is the size of the sensor in pixels and $\Npol$ is the number of polarities ($\Npol=2$ for the ON and OFF polarities coded in event-based cameras).

@@

Formally, let's define a layer of heterogeneous spiking neurons $\postsynaddr \in \postsynaddrspace$ by first describing how each neuron connects to presynaptic afferent from $\presynaddrspace$. In biology, a single cortical neuron has generally several thousands of synapses, and each synapse may be defined by its synaptic weight and its delay, that is, the time it takes for one spike to travel from the presynaptic neuron's soma to that of the postsynaptic neuron. A postsynaptic neuron $\postsynaddr \in \postsynaddrspace$ is then described by the synaptic weights connecting it to a presynaptic afferent from $\presynaddrspace$ but also by the set of possible delays. Note that a neuron may contact an afferent neuron with multiple different delays. For each neuron $\postsynaddr$, we thus define a set of $\Nsyn^\postsynaddr$ synapses, as  $\synapse^\postsynaddr = \{(\presynaddr^\postsynaddr_\ranksyn, \synapticweight^\postsynaddr_\ranksyn, \synapticdelay^\postsynaddr_\ranksyn)\}_{\ranksyn \in [1,\Nsyn^\postsynaddr]}$, where each synapse $\synapse^\postsynaddr_\ranksyn$ is associated to a weight $\synapticweight^\postsynaddr_\ranksyn$, a delay $\synapticdelay^\postsynaddr_\ranksyn$ and a presynaptic address $\presynaddr^\postsynaddr_\ranksyn$. This defines the full connectivity of the heterogeneous model. As a consequence, an event stream $\event_\presynaddrspace$ on the presynaptic address space is transformed by the synapse $\ranksyn$ of neuron $\postsynaddr$ into a new event stream $\event_{\presynaddrspace, \ranksyn}$ which is defined by 
$\{ (\presynaddr_\arank = 
 \presynaddr_\ranksyn^\postsynaddr, \timev=\timev_\arank + 
\synapticdelay_\ranksyn^\postsynaddr )_{ \arank \in [1,\numevent]\text{, }\ranksyn \in [1,\Nsyn^\postsynaddr]} )
\}$. This new stream of events \note{formaliser le multiplexage}
When post-synaptic neurons are activated on their soma by this spatio-temporal motif the discharge probability will increase, notably when these spikes converge on the soma in a synchronous manner.

>>>>

	    {\bf (a)}~Given a generic raster plot defined by a set of spikes occurring on specific neural addresses and at specific times, one may consider that this information consists of the repeated occurrence of precise spiking motifs. 
	    {\bf (b)}~We show the motifs used in this example, each identified at the top by a different color. To each of the $10$ neural adresses and $71$ different possible delays is assigned an evidence of activation (red) or deactivation (blue). Note that each afferent may be connected with multiple weights at different delays.
	    {\bf (c)}~The activation in time of the different motifs is then used to define a generative model for drawing a raster plot on the multi-unit address space: The propagation of the afferent information through these delays generates the raster plot seen in (a). 
	    {\bf (d)}~The inversion of the generative model provides with a model which gives the predicted probability of occurrence of each motif at any time and which may be used to generate a spike as a Bernoulli trial. The detection model yields in this particular case with an exact identification of the occurrence of motifs. Knowing the results of this detection, one may for illustration purposes highlight them by different colors in the raster plots, showing that in this synthetic examples, all spikes can be annotated with each identified spiking motif. 

@@

In neurobiological recordings or in the sensory signal obtained from an event-based camera, any generic raster plot consists of a stream of \emph{spikes} (see Figure~\ref{fig:model}-(a)). This can be formalized as a list (an ordered set) of neural addresses and timestamps  $\event = \{(\presynaddr_\arank, \timev_\arank)\}_{\arank \in [1,\numevent]}$ where $\numevent \in \mathbb{N} $ is the total number of events in the data stream and the rank $\arank$ is the index of each event in the list of events. Each event has a time of occurrence $\timev_\arank$  and an associated address $\presynaddr_\arank$ (which is typically in the form $(x_\arank, y_\arank, \polev_\arank)$ for event-based cameras). This defines an address space $\presynaddrspace$ which consists of the set of possible addresses. This can be the identified set of neurons in a neurobiological recording. For event-based cameras, it is denoted by $[1, \Nx]\times[1, \Ny] \times [1, \Npol] \subset \mathbb{N}^3$ where $(\Nx, \Ny)$ is the size of the sensor in pixels and $\Npol$ is the number of polarities ($\Npol=2$ for the ON and OFF polarities coded in event-based cameras).

@@

Let's formalize a layer of spiking neurons with heterogeneous delays (HD-SNN). Each neuron $\postsynaddr \in \postsynaddrspace$  connects to presynaptic afferent from $\presynaddrspace$. In biology, a single cortical neuron has generally several thousands of synapses, and each synapse may be defined by its synaptic weight and its delay, that is, the time it takes for one spike to travel from the presynaptic neuron's soma to that of the postsynaptic neuron. A postsynaptic neuron $\postsynaddr \in \postsynaddrspace$ is then described by the synaptic weights connecting it to a presynaptic afferent from $\presynaddrspace$ but also by the set of possible delays. Note that a neuron may contact an afferent neuron with multiple different delays. For each neuron $\postsynaddr$, we thus define a set of $\Nsyn^\postsynaddr$ synapses, as  $\synapse^\postsynaddr = \{(\presynaddr^\postsynaddr_\ranksyn, \synapticweight^\postsynaddr_\ranksyn, \synapticdelay^\postsynaddr_\ranksyn)\}_{\ranksyn \in [1,\Nsyn^\postsynaddr]}$, where each synapse $\synapse^\postsynaddr_\ranksyn$ is associated to a weight $\synapticweight^\postsynaddr_\ranksyn$, a delay $\synapticdelay^\postsynaddr_\ranksyn$ and a presynaptic address $\presynaddr^\postsynaddr_\ranksyn$. This defines the full connectivity of the heterogeneous model. As a consequence, an event stream $\event_\presynaddrspace$ on the presynaptic address space is transformed by the synapse $\ranksyn$ of neuron $\postsynaddr$ into a new event stream $\event_{\presynaddrspace, \ranksyn}$ which is defined by 
$\{ (\presynaddr_\arank = 
 \presynaddr_\ranksyn^\postsynaddr, \timev=\timev_\arank + 
\synapticdelay_\ranksyn^\postsynaddr )_{ \arank \in [1,\numevent]\text{, }\ranksyn \in [1,\Nsyn^\postsynaddr]} )
\}$. This new stream of events \note{formaliser le multiplexage}
When post-synaptic neurons are activated on their soma by this spatio-temporal motif the discharge probability will increase, notably when these spikes converge on the soma in a synchronous manner.
